---
title: "Cabbages"
author: "Tyler Hamblin"
date: "5 September 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
ttest_result <- t.test(VitC ~ Cult, data = veggy)

ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot(fill = "skyblue", color = "black", notch = TRUE, outlier.colour = "red") +
  labs(
    title = "Notched Box Plot of VitC by Cult",
    x = "Cultivation (Cult)",  # Updated x-axis label
    y = "Vitamin C (VitC)"     # Y-axis label
  ) +
  theme(plot.title = element_text(hjust = 0.5))  # Centered title

```

As shown in the box plot comparing levels of Vitamin C to two methods of Cultivation,c52 yields a higher result of Vitamin C. 

The appearance of the two boxes with one marginally higher than the other suggests a significance in the data that they are disjoint.   

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```

Again the difference of c39's 3rd Quartile results being smaller than c52's 1st Quartile suggests that the two methods are disjoint. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
p-value = 0.00000003405

This final test is more than sufficient evidence to conclude that these two methods of cultivation are very different from each other with one yielding higher Vitamin C results. The very minimal value of p is what allows me to make this inference from the information above. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

By asking ChatGPT we were able to get a string of R code that printed out a notched box plot showing the relationship of the two cultivation methods in comparison to their vitamin C yields. 

We then ran a favstats numerical comparison and a t-test that confirmed these results in a different layout and now we can be sure that this particular change in cultivation from c39 to c52 allows for more Vitamin C to be grown in the crops. 

These changes are directly related to one another and a level of Vitamin C typically suggests a certain cultivation method, still accounting for outliers, and a particular cultivation method can predict a higher/lower yield of Vitamin C.

